You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-25 paper/paper.tex
minor change

\subsection{Comparison Using Automatic Evaluation Metrics}
Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using previously the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics.

>>>>

\subsection{Comparison Using Existing Automatic Evaluation Metrics}
Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using previously the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics.
